Some forms of uncertainty may suppress the evolution of social learning

### 2022-04-23 ms.tex
updated figs with 1000 trials

Our primary outcome variable is the mean prevalence of the social learning
trait over $N=100$ agents in 100 trials at the final time step of each trial,
denoted $\meansl$.
Typically at the final time step all agents either have the social learning
trait or do not (see Supplement for a presentation of time series collections for
a representative sampling of \mt{TODO}).

>>>>

Our primary outcome variable is the mean prevalence of the social learning
trait over $N=100$ agents over 1000 trials at the final time step of each trial,
denoted $\meansl$.
Typically at the final time step all agents either have the social learning
trait or do not (see Supplement for a presentation of time series collections
and histograms of outcomes for
a representative sampling of variables \mt{TODO}).
